{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-04 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes
>w<, fixed shit and moved,added stuff

            \frac{q}{2}\Vert z - x^+\Vert^2 

@@

                0 &\le F(z) - F(\bar x) + \frac{L}{2}\Vert z - x\Vert - \frac{L}{2}\Vert z - \bar x\Vert^2. 

@@

        We introduce two examples variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.  
        MFISTA by Beck is an example of Definition \ref{def:generic-mapg-ls}. 
        % EXAMPLE | MFISTA WITH ARMIJO LINE SEARCH

@@

                    \STATE{\textbf{Input:} $x_0 \in \RR^n, L_0 \in \RR^n, f:\RR^n \rightarrow \RR, g: \mathbb \RR^n \rightarrow \overline \RR$} 

@@

                        $y_0 := x_0, t_0 := 1$.

@@

                        \STATE{$\tilde x_{k + 1} = T_{L_k^{-1}}(y_k)$.}

@@

            We now demonstrate that it's a special case of Definition \ref{def:generic-mapg-ls}.

@@

        Chambolle's backtracking strategies employs a line search strategies where the Lipschitz constant estimates increases if the descent lemma is satisfied. 
        % EXAMPLE | MFISTA WITH CAMBOLLE'S ADAPTIVE BACKTRACKING
        The following example illustrate Chambolle's adaptive backtracking strategy in the literatures with our GMAPG LS. 
        \begin{example}[MFISTA with Chambolle's adaptive backtracking]\;\\\vspace{-1em}
            This example won't give specific rules for calculating $\tilde x_k$ for monotone descent. 
            Chambolle's restart has specific rules for choosing the step sizes based on the estimates of the Lipschitz constants. 
            \begin{algorithm}[H]\label{alg:mfista-chambolle-ada}
                \STATE{\textbf{Input: } }
                \caption{MFISTA with Chambolle's adaptive backtracking}

>>>>

@@

                0 &\le F(z) - F(\bar x) + \frac{L}{2}\Vert z - x\Vert^2 - \frac{L}{2}\Vert^2 z - \bar x\Vert^2. 

@@

        \end{theorem}
        We introduce two examples variants of line search method used to enhance the accelerated proximal gradient methods in the literatures to demonstrate Definition \ref{def:generic-mapg-ls} and Theorem \ref{thm:gmapg-ls-convergence}.  
    \section{Algorithms formulations of GMAPG}
        MFISTA by Beck is an example of Definition \ref{def:generic-mapg-ls}. 
        % ======================================================================
        % EXAMPLE | MFISTA WITH ARMIJO LINE SEARCH
        % ======================================================================
        \begin{algorithm}[H]
            \begin{algorithmic}[1]
                \STATE{\textbf{Input:}}
                \caption{Armijo Line Search}
            \end{algorithmic}
        \end{algorithm}
        We will now give an algorithimic description of GMAPG. 
        \begin{algorithm}[H]\label{alg:chambolle-btls}
            \begin{algorithmic}[1]
                \STATE{\noindent
                    \textbf{Input:}
                    $f, g, x, v, L> L_{\min} > 0, \rho, \alpha$
                }
                \STATE{$L^+ := \max(L_{\min}, \rho L)$.}
                \FOR{$i = 1, 2, \ldots, 53$}
                    \STATE{$\alpha^+ := (1/2)\left(\alpha\sqrt{\alpha^2 + L/L^+} - \alpha^2\right)$. }
                    \STATE{$y^+ := \alpha^+ v + (1 - \alpha^+) x$. }
                    \STATE{$x^+ := T_{1/L^+, f, g}(y^+)$.}
                    \IF{$2D_f(x^+, y^+) \le \Vert x^+ - y^+\Vert^2$}
                        \STATE{\textbf{break}}
                    \ENDIF
                    \STATE{$L^+ := 2^iL^+$.}
                \ENDFOR
                \STATE{\textbf{Return: }$y^+, x^+, \alpha^+, L^+$}
                \caption{Chambolle's Backtracking}
            \end{algorithmic}
        \end{algorithm}

        \begin{algorithm}[H]\label{alg:mfista-chambolle-ada}
            \begin{algorithmic}[1]
                \STATE{\noindent
                    \textbf{Input:} $f, g, x_{-1}, L_0, r_{\min}, \text{Exit condition: }\mathbb E_\chi$. 
                }
            \caption{GMAPG with Chambolle's backtracking}

@@

                    \STATE{\textbf{Input:} $x_{-1} \in \RR^n, L_0 \in \RR^n, f:\RR^n \rightarrow \RR, g: \mathbb \RR^n \rightarrow \overline \RR$} 

@@

                        $x_0 := y_0, t_0 := 1$.

@@

                        \STATE{$\tilde x_{k + 1} := T_{L_k^{-1}}(y_k)$.}

@@

            We now demonstrate that Algorithm \ref{alg:mfista-armijo} is a special case of Definition \ref{def:generic-mapg-ls}.

@@
